Crossing Origins by Crossing Formats

### 2012-11-01 main.tex
abstract

\author{\IEEEauthorblockN{Jonas Magazinius}
\IEEEauthorblockA{Department of Computer Science\\
Chalmers University of Technology\\
Gothenburg, Sweden\\
jonas.magazinius@chalmers.se}
\and
\IEEEauthorblockN{Billy Rios}
\IEEEauthorblockA{dept. name of organization\\
name of organization, acronyms acceptable\\
City, United States of America\\
Email: name@xyz.com}
\and
\IEEEauthorblockN{Andrei Sabelfeld}
\IEEEauthorblockA{Department of Computer Science\\
Chalmers University of Technology\\
Gothenburg, Sweden\\
andrei@chalmers.se}
}

@@

\begin{abstract}

\end{abstract}

\begin{IEEEkeywords}
Web Security; Polyglot; Cross-domain;

\end{IEEEkeywords}

@@

\begin{lstlisting}[label=lst:php-sample,caption=Vulnerable PHP-program,captionpos=b]
<?php
session_start();
$_SESSION["secret"] = rand();
?>
<html><body>
Your guess: <?=$_GET["guess"]?>!
The secret is: <?=$_SESSION["secret"]?>
</body></html>
\end{lstlisting}
\begin{lstlisting}[label=lst:html-js,caption=Vulnerable PHP-program,captionpos=b]
<html><body>
Your guess: </body></html>;x=<html><body>!
The secret is: 521352342
</body></html>
\end{lstlisting}$

>>>>

% \author{\IEEEauthorblockN{Jonas Magazinius}
% \IEEEauthorblockA{Department of Computer Science\\
% Chalmers University of Technology\\
% Gothenburg, Sweden\\
% jonas.magazinius@chalmers.se}
% \and
% \IEEEauthorblockN{Billy Rios}
% \IEEEauthorblockA{dept. name of organization\\
% name of organization, acronyms acceptable\\
% City, United States of America\\
% Email: name@xyz.com}
% \and
% \IEEEauthorblockN{Andrei Sabelfeld}
% \IEEEauthorblockA{Department of Computer Science\\
% Chalmers University of Technology\\
% Gothenburg, Sweden\\
% andrei@chalmers.se}
% }

@@

\begin{abstract}
  In a heterogeneous system like the web, information is exchanged
  between components in versatile formats. A new breed of attacks is
  on the rise that exploit the mismatch between the expected and
  provided content. \emph{Injection attacks} are becoming increasingly
  more sophisticated by operating across multiple
  languages. \emph{Content repurposing} attacks supply malicious
  payload that appears formatted as benign content.
%
  This paper focuses on the root cause of a large class of attacks:
  \emph{polyglots}. A polyglot is a program that is valid in multiple
  programming languages. Polyglots allow multiple interpretation of
  the content, providing a new space of attack vectors. We
  characterize of what constitutes a dangerous format in the web
  setting and identify particularly dangerous formats, with PDF as the
  prime example. We demonstrate that polyglot-based attacks on the web
  open up for insecure communication across Internet origins. We
  perform a systematic study of PDF-based injection and content
  repurposing attacks. We evaluate the current practice in
  client/server content filtering and PDF readers for polyglot-based
  attacks, and report on vulnerabilities in the top 100 Alexa web sites.
  Our recommendations for protective measures on server side, in 
  browsers, and in PDF readers show how to mitigate the attacks.
\end{abstract}

\begin{IEEEkeywords}
Web Security; Polyglot; Injection; Cross-domain.
\end{IEEEkeywords}

@@

\begin{lstlisting}[label=lst:php-sample,caption=Vulnerable PHP-program,captionpos=b]
<?php
session_start();
$_SESSION["secret"] = rand();
?>
<html><body>
Your guess: <?=$_GET["guess"]?>!
The secret is: <?=$_SESSION["secret"]?>
</body></html>
\end{lstlisting}
\begin{lstlisting}[label=lst:html-js,caption=Vulnerable PHP-program,captionpos=b]
<html><body>
Your guess: </body></html>;x=<html><body>!
The secret is: 521352342
</body></html>
\end{lstlisting}
\if 0
$
\fi
